\documentclass[11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{hyperref}

\address{[Name Placeholder]\\
[Institution Placeholder]\\
[Address Placeholder]\\
\href{mailto:[mail placeholder]}{[mail placeholder]}}

\date{\today}

\begin{document}
\begin{letter}{Editor-in-Chief\\Engineering Applications of Artificial Intelligence\\Elsevier}
\opening{Dear Editor-in-Chief,}

Please find enclosed our manuscript entitled \textbf{``Robustness Benchmarking of Embedded Battery State Estimation: A Measurement-Only Comparison of Coulomb Counting, Hybrid ECM, and Data-Driven SOC/SOH Models''}. This cover letter is a structured placeholder and should be replaced by polished prose before submission.

\begin{itemize}
    \item Bullet: introduce the paper as a robustness-focused comparison of battery state estimators for embedded BMS deployment.
    \item Bullet: emphasize the comparison of CC, CC+SOH, ECM, and SOC+SOH under measurement-only perturbations.
    \item Bullet: state the main novelty as the separation of estimator families under realistic sensor corruption and timing faults.
    \item Bullet: mention the practical contribution: a decision-oriented benchmark rather than only a clean-data accuracy report.
    \item Bullet: mention that the study is directly relevant to embedded AI and industrial energy-storage applications.
\end{itemize}

We confirm that the manuscript is not under consideration elsewhere. Author details and compliance statements should be inserted here before submission.

\closing{Sincerely,}
[Signature Placeholder]
\end{letter}
\end{document}
